Improving the Replicability of Psychological Science Through Pedagogy

### 2016-09-23 paper/paper.Rmd
removed direct from replications

abstract: 
    "Replications are important to science, but who will do them? One proposal is that students can conduct direct replications as part of their training. As a proof-of-concept for this idea, here we report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course. Congruent with previous studies, replications typically yielded smaller effects than originals: The modal outcome was partial support for the original claim. This work documents the challenges facing motivated students in reproducing previously published results on a first attempt. We describe the workflow and pedagogical methods that were used in the class and discuss challenges both for the adoption of this pedagogical model and for replication research more broadly."

@@

Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012]. Yet under the current incentive structure for science, direct replication is not typically valued. One potential solution to this problem is to make direct replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012]. Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy.

@@

We also describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy. Although mentorship in specific experimental methods is an important part of the standard advising relationship, the classroom context allows for elucidation of general principles of good research and discussion of how they can be modified to fit specific instances. And replication research specifically illustrates a number of important concepts -- experimental design, power analysis, reporting standards, and preregistration, among others -- in a way that more open-ended projects, which require new conceptual development, often do not [see @frank2012 for a more extended argument]. There are significant limitations on what can be done in a single term, within the constraints of a course budget and the instructors' expertise, and we return to these in the Discussion. Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole would be considerable.

>>>>

abstract: 
    "Replications are important to science, but who will do them? One proposal is that students can conduct replications as part of their training. As a proof-of-concept for this idea, here we report a series of 11 pre-registered replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course. Congruent with previous studies, replications typically yielded smaller effects than originals: The modal outcome was partial support for the original claim. This work documents the challenges facing motivated students in reproducing previously published results on a first attempt. We describe the workflow and pedagogical methods that were used in the class and discuss challenges both for the adoption of this pedagogical model and for replication research more broadly."

@@

Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012]. Yet under the current incentive structure for science, replication is not typically valued. One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012]. Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy.

@@

We also describe our process for conducting replications as part of classroom pedagogy. Although mentorship in specific experimental methods is an important part of the standard advising relationship, the classroom context allows for elucidation of general principles of good research and discussion of how they can be modified to fit specific instances. And replication research specifically illustrates a number of important concepts -- experimental design, power analysis, reporting standards, and preregistration, among others -- in a way that more open-ended projects, which require new conceptual development, often do not [see @frank2012 for a more extended argument]. There are significant limitations on what can be done in a single term, within the constraints of a course budget and the instructors' expertise, and we return to these in the Discussion. Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole would be considerable.
